Preprocessing: filtering

### 2022-09-27 analysis/preprocessor/filtering.Rmd
add information about corrected responses
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

- Extra notes
- Missing notes
- Substituted notes

@@

```{r, include = FALSE, eval = FALSE}
dt_correct_onset_1 <- fread(here("filtered", "dt_correct_onset_1.txt"))
dt_correct_onset_2 <- fread(here("filtered", "dt_correct_onset_2.txt"))
dt_correct_onset_3 <- fread(here("filtered", "dt_correct_onset_3.txt"))
dt_correct_onset_4 <- fread(here("filtered", "dt_correct_onset_4.txt"))
dt_correct_onset_5 <- fread(here("filtered", "dt_correct_onset_5.txt"))

@@

>>>>

- Extra notes (Onset: `r round(nrow(error_extra_onset)/(20*16)*100, 2)` %, Offset: `r round(nrow(error_extra_offset)/(20*16)*100, 2)` %)
- Missing notes (Onset:  `r round(nrow(error_missing_onset)/(20*16)*100, 2)` %, Offset: `r round(nrow(error_missing_offset)/(20*16)*100, 2)` %)
- Substituted notes (Onset: `r round(nrow(error_sub_offset)/(20*16)*100, 2)` %, Offset: `r round(nrow(error_sub_offset)/(20*16)*100, 2)` %)

@@

```{r, include = FALSE}
dt_correct_onset_1 <- fread(here("filtered", "dt_correct_onset_1.txt"))
dt_correct_onset_2 <- fread(here("filtered", "dt_correct_onset_2.txt"))
dt_correct_onset_3 <- fread(here("filtered", "dt_correct_onset_3.txt"))
dt_correct_onset_4 <- fread(here("filtered", "dt_correct_onset_4.txt"))
dt_correct_onset_5 <- fread(here("filtered", "dt_correct_onset_5.txt"))

@@

# Corrected responses
```{r, include = FALSE}
extra_onset <- sum(as.numeric(error_extra_onset[CorrectionNr != "Check individually"]$CorrectionNr))
extra_offset <- sum(as.numeric(error_extra_offset[CorrectionNr != "Check individually"]$CorrectionNr))
missing_onset <- sum(as.numeric(error_missing_onset[CorrectionNr != "Check individually"]$CorrectionNr))
missing_offset <- sum(as.numeric(error_missing_offset[CorrectionNr != "Check individually"]$CorrectionNr))
sub_onset <- sum(as.numeric(error_sub_onset[CorrectionNr != "Check individually"]$CorrectionNr))
sub_offset <- sum(as.numeric(error_sub_offset[CorrectionNr != "Check individually"]$CorrectionNr))
mixed_onset <- sum(as.numeric(error_ind_onset$CorrectionNr))
mixed_offset <- sum(as.numeric(error_ind_offset$CorrectionNr))
```

- Extra notes (Onset: `r extra_onset`, Offset: `r extra_offset`)
- Missing notes (Onset: `r missing_onset`, Offset: `r missing_offset`)
- Substituted notes (Onset: `r sub_onset`, Offset: `r sub_offset`)
- Mixed (Onset: `r mixed_onset`, Offset: `r mixed_offset`)
- Total (Onset: `r sum(extra_onset, missing_onset, sub_onset, mixed_onset)`, Offset: `r sum(extra_offset, missing_offset, sub_offset, mixed_offset)`)
- In total, `r round(sum(extra_onset, missing_onset, sub_onset, mixed_onset)/nrow(dt_onset)*100, 2)` % for onsets and `r round(sum(extra_offset, missing_offset, sub_offset, mixed_offset)/nrow(dt_offset)*100, 2)` % for offsets are corrected.
